% !TeX root = Report.tex
\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amsmath}
\title{Moneyworth Web App Project Report}
\author{Group Members: Name1, Name2, Name3, Name4}
\date{\today}

\begin{document}
\maketitle

\section{Introduction}
Moneyworth is a web application designed to help users manage and browse sales listings. The main features include user authentication, a dashboard, browsing and creating sales, and profile management. The application provides a modern, responsive interface with a navigation bar, hero section on the Home page, and a footer on all pages. Key pages include Home, Dashboard, Browse Sales, Create Sale, About, and Contact.

\section{Part a: HTML and Django Template Code Implementation}
This section presents the HTML and Django template code used for the project layout.

\subsection{Base Template Explanation}
The base template, \texttt{base.html}, defines the overall structure of the site. It includes a navigation bar, a hero (jumbotron) section (on the Home page), and a footer. Content blocks are defined using Django's template block tags, allowing child templates to override specific sections.

\begin{verbatim}
<!-- templates/core/base.html -->
<!DOCTYPE html>
<html lang="en">
<head>
    <meta charset="UTF-8">
    <title>{% block title %}Django Sales App{% endblock %}</title>
    <link rel="stylesheet" href="{% static 'css/bootstrap.min.css' %}">
    <link rel="stylesheet" href="{% static 'css/bootstrap-icons.min.css' %}">
    {% block extra_head %}{% endblock %}
</head>
<body>
    <nav>...navbar code...</nav>
    {% block content %}{% endblock %}
    <footer>...footer code...</footer>
    <script src="{% static 'js/bootstrap.bundle.min.js' %}"></script>
</body>
</html>
\end{verbatim}

\subsection{Child Template Example}
A child template, such as \texttt{home.html}, extends the base template and fills in the content block:

\begin{verbatim}
<!-- templates/core/home.html -->
{% extends 'core/base.html' %}
{% block title %}Home - Django Sales App{% endblock %}
{% block content %}
<div class="jumbotron">
    <h1>Welcome to the Django Sales App!</h1>
    <p>Browse and manage sales listings easily.</p>
</div>
{% endblock %}
\end{verbatim}

\subsection{Use of Template Tags}
Key Django template tags used include:
\begin{itemize}
    \item \verb|{% extends %}|: Allows a template to inherit from a base template.
    \item \verb|{% block %}|: Defines sections that child templates can override.
    \item \verb|{% static %}|: Resolves the URL for static files (CSS, JS, images).
\end{itemize}
These tags help organize templates, promote code reuse, and simplify static file management.

\subsection{Bonus: URL and View Structure}
The \texttt{urls.py} and \texttt{views.py} files connect URLs to views and templates. For example:

\begin{verbatim}
# core/urls.py
from django.urls import path
from . import views

urlpatterns = [
    path('', views.home, name='home'),
    path('dashboard/', views.dashboard, name='dashboard'),
    path('sales/', views.browse_sales, name='browse_sales'),
    path('sales/create/', views.create_sale, name='create_sale'),
    path('about/', views.about, name='about'),
    path('contact/', views.contact, name='contact'),
]

# core/views.py
from django.shortcuts import render

def home(request):
    return render(request, 'core/home.html')
# ...other view functions...
\end{verbatim}

\section{Part b: Benefits of Django for Responsive Web Apps}
Django is ideal for building responsive web applications due to its template system, which separates logic from presentation. It integrates easily with CSS frameworks like Bootstrap, enabling mobile-friendly designs. Django also provides built-in security, scalability, and rapid development features, making it suitable for modern web apps.

\section{Part c: Linking Static CSS and JavaScript in Django}
To include static files in Django:
\begin{enumerate}
    \item Set \texttt{STATIC\_URL} in \texttt{settings.py} (e.g., \texttt{STATIC\_URL = '/static/'}).
    \item Add \verb|{% load static %}| at the top of each template.
    \item Reference static files using \verb|{% static 'css/bootstrap.min.css' %}| or similar.
\end{enumerate}
Example:
\begin{verbatim}
{% load static %}
<link rel="stylesheet" href="{% static 'css/bootstrap.min.css' %}">
\end{verbatim}

\section{Part d: Components of MTV Architecture in Django}
Django follows the Model-Template-View (MTV) architecture:
\begin{itemize}
    \item \textbf{Model:} Defines data structure. E.g., the Sales model in \texttt{core/models.py} manages product data.
    \item \textbf{View:} Handles requests and returns responses. E.g., functions in \texttt{core/views.py} render templates for each page.
    \item \textbf{Template:} Renders HTML. E.g., files in \texttt{templates/core/} display content to users.
\end{itemize}

\end{document}
